State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-13 prism-backend/research/soa_review/ac.tex
Added review of CL11. AC based on aggregate signatures.

@@

@@

The system in \cite{aks12} also uses BBS+ signatures as a main building block
to design a system with accountable anonymity, although it is not ``strictly''
an anonymous credentials system: users receive a credential that lets them
authenticate anonymously against service providers, but this credential does
not include attributes, which seems to be the common case in ACs (however,
with BBS+ it is trivial to add attributes, although this should be modelled).
The main contribution of \cite{aks12} is the design and incorporation of
protocols to block misbehaving users depending on their behaviour, without
relying on trusted third parties. This is based on ``reputation lists'',
maintained by each service provider. Uses that have previously registered
with a Group Manager can authenticate against service providers by proving
knowledge of a valid credential. Depending on how these users behave during
the session with the service provider, the latter adds the interaction to
either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
subsequent authentications, users prove (in an ``almost unlinkable'' way
w.r.t. previous authentications) that they have a certain reputation,
computed as a weighted sum of their presence in the good/bad behaviour
lists. Moreover, each service provider can maintain multiple thematic lists,
and then require users to satisfy arbitrary boolean policies based on these
lists (e.g., reputation $\gt X_1$ on $list_1$ and reputation $\lt X_2$ on
$list_2$ or reputation $\eq X_3$ on $list_3$) so that only users meeting
the defined policy can access their system. These proves have though a linear
dependency on the number of authentications that each user has done in
the past. To reduce the impact of this, the authors create epochs. When a
user authenticates successfully against a service provider, at a given epoch
$i$, the service provider gives the user a token that authenticates the
reputation that the user had at epoch $i$. Then, when this user tries to
authenticate again, he only needs to give that token, and prove his reputation
since epoch $i$ (this is why authentication is ``almost unlinkable'', as
service providers may learn when the user authenticated for the last time).
Note that no trusted party is involved in the blacklisting process, as
correctness of all tokens exchanged between users and service providers to prove
meeting certain policy, is ensured via the corresponing proof protocols.
Concerning security, the system is proven secure in the simulation paradigm,
claiming to meet (informally defined) properties of:

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}

@@

>>>>

\item[\cite{cl11}:] The approach differs from the conventional ones. In this
  case, the focus is on settings where users may want to combine multiple
  credentials from different issuers. Thus, interest is on reducing the size
  of the resulting credentials, and the efficiency of associated processes.
  The approach is based on aggregate signatures. As usual, each credential
  may contain several attributes. Each attribute is independently signed
  by the issuer. Then, users can combine an arbitrary number of signed
  attributes (by the same or different issuers) into a single aggregate
  signature. Verification only needs the aggregated signature and the set
  of public keys of all the involved issuers. To prevent different users
  from aggregating their credentials, the authors resort to \emph{indexed}
  aggregate signatures: an index is added to each signature, such that only
  signatures that have the same index can be aggregated. In their instantiation,
  the signature is a BGLS signature \cite{bgls03}, and the index is a BB
  signature \cite{bb04}. The actual instantiation seems impractical (too many
  linear costs, see the table in the paper).

@@

\item[\cite{cl11}:] The security properties in this work are unforgeability
  and anonymity, for which the authors give game-based definitions.

@@

The system in \cite{aks12} also uses BBS+ signatures as a main building block
to design a system with accountable anonymity, although it is not ``strictly''
an anonymous credentials system: users receive a credential that lets them
authenticate anonymously against service providers, but this credential does
not include attributes, which seems to be the common case in ACs (however,
with BBS+ it is trivial to add attributes, although this should be modelled).
The main contribution of \cite{aks12} is the design and incorporation of
protocols to block misbehaving users depending on their behaviour, without
relying on trusted third parties. This is based on ``reputation lists'',
maintained by each service provider. Uses that have previously registered
with a Group Manager can authenticate against service providers by proving
knowledge of a valid credential. Depending on how these users behave during
the session with the service provider, the latter adds the interaction to
either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
subsequent authentications, users prove (in an ``almost unlinkable'' way
w.r.t. previous authentications) that they have a certain reputation,
computed as a weighted sum of their presence in the good/bad behaviour
lists. Moreover, each service provider can maintain multiple thematic lists,
and then require users to satisfy arbitrary boolean policies based on these
lists (e.g., reputation $\ge X_1$ on $list_1$ and reputation $\le X_2$ on
$list_2$ or reputation $= X_3$ on $list_3$) so that only users meeting
the defined policy can access their system. These proves have though a linear
dependency on the number of authentications that each user has done in
the past. To reduce the impact of this, the authors create epochs. When a
user authenticates successfully against a service provider, at a given epoch
$i$, the service provider gives the user a token that authenticates the
reputation that the user had at epoch $i$. Then, when this user tries to
authenticate again, he only needs to give that token, and prove his reputation
since epoch $i$ (this is why authentication is ``almost unlinkable'', as
service providers may learn when the user authenticated for the last time).
Note that no trusted party is involved in the blacklisting process, as
correctness of all tokens exchanged between users and service providers to prove
meeting certain policy, is ensured via the corresponing proof protocols.
Concerning security, the system is proven secure in the simulation paradigm,
claiming to meet (informally defined) properties of:

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\end{itemize}

@@

How to compare efficiency of AC systems?
